### 2021-09-01 documentos/pce.tex
muevo ecuaciones de dilatacion y semigrupo

A remarkable consequence of positivity 
\subsection{Single qubit case} % {{{
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\sa g
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i
\end{equation}

with
\begin{equation}
\mcL_\alpha[\Delta]:= \frac{\gamma}{2}\left( \sigma_\alpha \Delta \sigma_\alpha -\Delta \right).
\label{eq:1qubit_semigroup}
\end{equation}
We will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
\begin{equation}
\mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
\label{eq:Nqubit_semigroup}
\end{equation}

\begin{align}
U_\alpha\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_\alpha \ket{\psi}\ket{1} \right)\\
U_\alpha\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_\alpha \ket{\psi}\ket{1} \right)
\label{eq:1qubit_stinespring}
\end{align}
similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)\\
U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)
\label{eq:Nqubit_stinespring}
\end{align}

@@

Let us now define a Pauli component erasing (PCE) operation. A linear operation 
$\mcE$ that acts on a density matrix $\rho$ of a system of qubits is a PCE operation if 
it transforms the Pauli components of $\rho$ as 
\begin{equation}
\begin{split}
	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{split}
\end{equation}
A PCE operation is a trace-preserving operation that leaves invariant or erases 
the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
todo claro y no hay problema en dejarlo así por el momento.}

>>>>

A remarkable consequence of positivity 
\subsection{Single qubit case} % {{{
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i r_i
\end{equation}
where $\tau_k$ is either $1$ or $0$. A direct evaluation of the

with
\begin{equation}
\mcL_\alpha[\Delta]:= \frac{\gamma}{2}\left( \sigma_\alpha \Delta \sigma_\alpha -\Delta \right).
\label{eq:1qubit_semigroup}
\end{equation}
We will show later that this can be trivially generalized to the $N$ qubit case.

\begin{align}
U_\alpha\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_\alpha \ket{\psi}\ket{1} \right)\\
U_\alpha\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_\alpha \ket{\psi}\ket{1} \right)
\label{eq:1qubit_stinespring}
\end{align}
similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case.

@@

Let us now define a Pauli component erasing (PCE) operation. A linear operation 
$\mcE$ that acts on a density matrix $\rho$ of a system of qubits is a PCE operation if 
it transforms the Pauli components of $\rho$ as 
\begin{equation}
\begin{split}
	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{split}
\end{equation}
\ddnote{hay un typo en esta ecuacion}
A PCE operation is a trace-preserving operation that leaves invariant or erases 
the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
todo claro y no hay problema en dejarlo así por el momento.}
